\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-08-25 ase20/main.tex
[ASE] Merged Section 4 & 5
Added authors / Removed review style
Added copyright / Shorten author info / Relocated figures/tables
Added Acknowledgements for NRF / Updated report

\documentclass[sigconf,review,anonymous]{acmart}

\usepackage{url}
\usepackage{amsmath, amssymb}
\usepackage{natbib}
\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

@@

\author{Jihyeok Park}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{jhpark0223@kaist.ac.kr}

\author{Jihee Park}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{j31d0@kaist.ac.kr}

\author{Sukyoung Ryu}
\affiliation{%
  \institution{KAIST}
  \department{School of Computing}
  \city{Daejeon}
  \country{South Korea}
}
\email{sryu.cs@kaist.ac.kr}

@@

\input{intro}
\input{overview}
\input{parser}
\input{compiler}
\input{impl}
\input{eval}
\input{related}
\input{conclusion}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{url}
\usepackage{amsmath, amssymb}
\usepackage{natbib}
\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}
\usepackage{makecell}

@@

% copyright
\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmcopyright}\acmConference[ASE '20]{35th IEEE/ACM International Conference on Automated Software Engineering}{September 21--25, 2020}{Virtual Event, Australia}
% \acmBooktitle{35th IEEE/ACM International Conference on Automated Software Engineering (ASE '20), September 21--25, 2020, Virtual Event, Australia}
\acmPrice{15.00}
\acmDOI{10.1145/3324884.3416632}
\acmISBN{978-1-4503-6768-4/20/09}

@@

\author{Jihyeok Park}
\affiliation{%
  \institution{KAIST, South Korea}
}
\email{jhpark0223@kaist.ac.kr}

\author{Jihee Park}
\affiliation{%
  \institution{KAIST, South Korea}
}
\email{j31d0@kaist.ac.kr}

\author{Seungmin An}
\affiliation{%
  \institution{KAIST, South Korea}
}
\email{h2oche@kaist.ac.kr}

\author{Sukyoung Ryu}
\affiliation{%
  \institution{KAIST, South Korea}
}
\email{sryu.cs@kaist.ac.kr}

@@

\input{intro}
\input{overview}
\input{parser}
\input{compiler}
\input{eval}
\input{related}
\input{conclusion}

\section*{Acknowledgements}
This work was supported by National Research Foundation of
Korea (NRF) (Grants NRF-2017R1A2B3012020 and 2017M3C4A7068177).
